### 2021-12-19 documentos/kraus.tex
dandole

PCE channels can also be described with \textit{simple collision models}~\cite{Ziman2010}. To prove this, observe that PCEGs can always be implemented using an unitary over the system and an ancilla~\cite{Stinespring2006}. Since PCEG always have Kraus rank $2$, one can always choose a qubit as the ancillary system, concretely,
\begin{equation}
\mcG_{\vec \alpha}[\rho]:=\tr_{\text{qubit}} \left( U_{\vec \alpha} \left(\rho\otimes \projj{0}\right) U^\dagger{}_{\vec \alpha} \right),
\end{equation}
where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with the unitary defined as,
\begin{align}
U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right),\\
U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right).
\label{eq:Nqubit_stinespring}
\end{align}
Therefore, any concatenation of PCEGs can be described as a collision model with as many collisions as generators needed. In fact, generators are described with one collision. For the general case, consider some PCE channel $\mcE$ generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots, \mcG_{\vec \alpha_M} \right\}$. For this, we have an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$ (or equivalently, one qubit with the additional assumption that its state is reset to $\ket{0}$ after each collision). The collision with the $k\text{th}$ particle is described by $U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$ particle. Therefore $\mcE$ can be written as follows,
\begin{equation}
\mcE[\rho]=\tr_{\text{E}} \left( \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M}\right)\left( \rho \otimes \projj{0}^{\otimes M}\right) \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M} \right)^\dagger{} \right),
\end{equation}
where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits. Notice that as PCEGs commute, the order of the collisions can be changed, taking care also of the order of the partial traces.
\begin{itemize}
\item Relate to decoherence, for PCEG\ddnote{hecho}
\item Play with non PCEG PCEs\ddnote{hecho}
\item Dependiendo de si sale algo bonito, podemos poner algun modelo en
particular para todos los canales (sistema central + ambiente). Seria de buscar
dilataciones sencillas y razonables por lo menos a los canales generadores.\ddnote{hecho, es el asunto de collision models}
\todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
\end{itemize}

>>>>

PCE channels can also be described with \textit{simple collision models}~\cite{Ziman2010}. To prove this, observe that PCEGs can always be implemented using an unitary over the system and an ancilla~\cite{Stinespring2006}. Since PCEG always have Kraus rank $2$, one can always choose a qubit as the ancillary system, concretely,
\begin{equation}
\mcG_{\vec \alpha}[\rho]:=\tr_{\text{qubit}} \left( U_{\vec \alpha} \left(\rho\otimes \projj{0}\right) U^\dagger{}_{\vec \alpha} \right),
\end{equation}
where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with the unitary defined as,
\begin{align}
U_{\vec\alpha}\ket{\psi} \ket{0}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right),\\
U_{\vec\alpha}\ket{\psi} \ket{1}:=\frac{1}{\sqrt{2}} \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right).
\label{eq:Nqubit_stinespring}
\end{align}
Therefore, any concatenation of PCEGs can be described as a collision model with as many collisions as generators needed. In fact, generators are described with one collision. For the general case, consider some PCE channel $\mcE$ generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots, \mcG_{\vec \alpha_M} \right\}$. For this, we can define an environment consisting of $M$ qubits initially in the state $\left( \projj{0} \right)^{\otimes M}$ (or equivalently, one qubit with the additional assumption that its state is reset to $\ket{0}$ after each collision). The collision with the $k\text{th}$ particle is described by $U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$ particle. Therefore $\mcE$ can be written as follows,
\begin{equation}
\mcE[\rho]=\tr_{\text{E}} \left( \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M}\right)\left( \rho \otimes \projj{0}^{\otimes M}\right) \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M} \right)^\dagger{} \right),
\end{equation}
where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits. Notice that as PCEGs commute, the order of the collisions can be changed, taking care also of the order of the partial traces.
\begin{itemize}
\item Relate to decoherence, for PCEG\ddnote{hecho}
\item Play with non PCEG PCEs\ddnote{hecho}
\item Dependiendo de si sale algo bonito, podemos poner algun modelo en
particular para todos los canales (sistema central + ambiente). Seria de buscar
dilataciones sencillas y razonables por lo menos a los canales generadores.\ddnote{hecho, es el asunto de collision models}
\todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
\end{itemize}
